Model Based Systems Engineering with a Docs-as-Code Approach for the SeaLion CubeSat Project

### 2023-04-24 manuscript/references.tex
Address peer comments and MDPI comments in manuscript

>>>>

    \bibitem{linkml}Mungall, C. LinkML model your data. {\em LinkML}., https://linkml.io/
    \bibitem{younse_cameron_bradley_2021}Younse, P., Cameron, J. \& Bradley, T. Comparative analysis of model-based and traditional systems engineering approaches for architecting a robotic space system through Automatic Information Transfer. {\em IEEE Access}. \textbf{9} pp. 107476-107492 (2021)
    \bibitem{call_herber_2022}Call, D. \& Herber, D. Applicability of the diffusion of innovation theory to accelerate model-based systems engineering adoption. {\em Systems Engineering}. \textbf{25}, 574-583 (2022)
    \bibitem{mazzini}Mazzini, S., Tronci, E., Paccagnini, C. \& Olive, X. A Model-Based methodology to support the Space System Engineering (MBSSE). {\em ERTS2 2010, Embedded Real Time Software \& Systems}. (2010,5), https://hal.science/hal-02267836
    \bibitem{esa}ESA Model-based system engineering. , https://www.esa.int/Enabling\_Support/Preparing\_for\_the\_Future/Discovery\_and\_Preparation/Model-based\_system\_engineering
    \bibitem{nottage_corns_2012}Nottage, D. \& Corns, S. Application of model-based systems engineering on a university satellite design team. {\em Procedia Computer Science}. \textbf{8} pp. 207-213 (2012)
    \bibitem{kaslow}Kaslow, D., Ayres, B., Cahill, P., Hart, L. \& Yntema, R. Developing a CubeSat Model-Based System Engineering (MBSE) reference model — Interim status \#3. {\em 2017 IEEE Aerospace Conference}. pp. 1-15 (2017)
    \bibitem{structurizr}Structurizr Software architecture models as code. {\em Structurizr}., https://structurizr.org/
    \bibitem{f_prime_prime}Bocchino, R., Levison, J. \& Starch, M. FPP: A Modeling Language for F Prime. {\em 2022 IEEE Aerospace Conference (AERO)}. pp. 1-15 (2022)
    \bibitem{f_prime}NASA F' a flight software and embedded systems framework. {\em F'}., https://nasa.github.io/fprime/

### 2023-04-24 manuscript/template.tex
Address peer comments and MDPI comments in manuscript

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Kevin Chiu, Sean Marquez and Sharanabasaweshwara Asundi}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The SeaLion flight architecture team for the SeaLion CubeSat project used a model based system engineering with docs-as-code approach to improve planning and organization of the project.  This was done in response to the growing number of University CubeSat teams with untrained students and personnel.  The team created tools for the systems architecture with the Mach 30 Modeling Language to create a architecture that is easy to learn and use even for newly admitted team members with little to no training. These tools can also generate documents via its own code for easy presentaton on a local file system without any proprietary software.}

@@

Presented here is the systems engineering approach of the SeaLion CubeSat mission architecture.  This includes the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, and implementation of the SeaLion mission architecture for the flight software using a model-based approach.  Through, model-based systems engineering (MBSE), the SeaLion flight software team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.  These models were used to conduct activities such as design, specification, analysis, verification and validation of the system.  This was done by applying the NASA handbook on systems engineering \cite{nasa_handbook} to CubeSat mission design in efforts to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.

\subsection{CubeSat}
The CubeSat, originating from California Polytechnic State University in 1999, are a standardized form of nanosatellites.  Nanosatellites are satellites typically defined with a mass of less than 10 kg.  CubeSats, also known as Cube Satellites, are defined by the standardized and modular architecture of 1-Unit (1U) cube with dimensions of 10 cm X 10 cm X 10 cm with a mass of up to 2 kg \cite{cds_rev14}.  They can be scaled to 2-Units (2U), 3-Units (3U), or higher depending on units added as shown in figure \ref{fig:cubesat_family} with sizes designated by the CubeSat specification \cite{cds_rev14}.  This is done by the additional of standardized cube units to upscale the CubeSat.  The ability to scale by modularity gives a highly standardized structure for ease of expansion to provide versatility in functionality.  Due to their small size, mass, and lack of dedicated launch vehicles, CubeSats are typically launched as secondary payloads in conjunction with other larger satellites, informally known as “piggy-backing”.  This greatly decreases the cost of launching a CubeSat which greatly increases the accessibility of inserting objects into space.

@@

The SeaLion flight software team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team.  Three separate payloads require care and attention to ensure success.  The results of this effort are presented in this article.

@@

To address some of these issues, the SeaLion flight software team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.  These provided system engineering approaches and tools include factors such as planning, documentation, project management, and simplifying the process.  Special attention should be given to systems engineering and information exchange for multidisciplinary teams \cite{aalto}.  To showcase these factor's importance, a survey conducted, by University of Bristol, on how to set up CubeSat projects of forty CubeSat groups emphasized the following relevant lessons learned \cite{howtosetup}:

@@

A MBSE approach was adopted by the Sealion CubeSat flight software team since it provided benefits such as reducing the ambiguity that usually comes with using informal language to specify systems or its various aspects.  It also minimized the duplication of content that tends to accumulate in a document-based system engineering approach.

Proper adoption of a MBSE approach also includes the selection of modeling language and modeling tool.  Considerations when selecting the modeling language and tool was overhead incurred from training the team, the technical overhead of setting up modelling tools, and future adaptability.  Refer to table \ref{tab:language} for modelling language down selection overview.  In addition, the Sealion CubeSat flight software team eventually decided to adopt a docs-as-code approach to further enhance the MBSE approach to achieve the listed goals shown above.

@@

Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.  Information in a traditional systems engineering approach today is mostly captured informally, not authored based on a methodology, configuration managed in silo tools, adhocly and infrequently integrated, not easily traceable to its provenance, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.  These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.

In contrast, a MBSE approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.  Models provide the following key advantages over document-based approaches \cite{ibm_mbse}:

@@

\subsection{Docs-As-Code Approach}
Docs-as-code refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.  This allows for documentation to updated seamlessly without additional work with document tools (doctools).  The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio), etc.  To do so would mean that the “following the same workflows as development teams, and being integrated in the product team. It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{ibm_mbse}.  The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{ibm_mbse}.  In addition, these models can stored and used persistently on a local file system without the use of cloud based services.  Proprietary services are not required to generate documentation, modify documentation, or modify models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modelling Language and Methodology}
The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the flight software team conducting a trade study to determine the most suitable.  The down selection criteria that the SeaLion CubeSat flight software team has taken into consideration is shown in table \ref{tab:language}.

@@

\subsection{Ontological Modeling Language}
M30ML was developed using the Ontological Modeling Language (OML) as its basis.  OML is a language that enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}.  OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of aforementioned standard for use in systems engineering \cite{oml_language}.  OWL2 does not conform easily to individual modelling rules without tooling support; thus, OML was created.  OML is a tool to improve the speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.

@@

\subsection{Document Generation}
As noted multiple times throughout this article, there have been a number of figures and tables generated from the YAML files placed within the SeaLion mission architecture GitHub repository.  Many of the figures are UML diagrams that are auto-generated artifacts rendered from the M30ML modeling language and formatted using the Liquid template language.  This is the link for the docs-as-code approach.  YAML code files are used to generate documents for information sharing between group members.  This means that any changes made to the SeaLion mission architecture model can immediately be used to generate new documents.  Whether it be diagrams, tables, or text, continuous updating is ensured that any changes affecting dependencies within the mission architecture are kept in sync.  A conference proceeding manuscript presented in AIAA SciTech 2023 was created purely by a docs-as-code format \cite{scitech_proceeding}.  The team used a LaTeX template to automatically format the manuscript to the conference guidelines and subsequently inject items such as the generated diagrams, tables, and references directly into the manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Component Implementation}
The implementation of M30ML for components is still a work in progress at the time of this article's publication.  A brief description of current component implementation into the SeaLion model is provided.  However, many of the implementation methods mentioned herein are subjected to change and are not finalized unlike the architecture described in the prior section.

\subsection{Distributed OSHW Framework}
The M30ML pillars are based on Open Source Hardware (OSHW) principals \cite{mach30_git}.  The current SeaLion mission architecture repository, at time of article publication, for components is “structured as a Distributed OSHW Framework (DOF) - component for defining the contents of the Mission concept of operations (ConOps) as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs) and assembly instructions for the SeaLion CubeSat” \cite{sealion_mission_architecture}.  Inside the components folder of the SeaLion mission architecture repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.  Each of those folders would contain a components folder and subsequently those individual labeled components can have their own components folder.  Thus, a chain of components and subcomponents can be created as illustrated in figure \ref{fig:components_file}.  A parts YAML file in each components folder details what the subcomponents would be.  An excerpt example for the main SeaLion cubesat is provided in figure \ref{fig:components} that is associated with the file folders shown in figure \ref{fig:components_file}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
The SeaLion flight software team used MBSE with docs-as-code approach to the SeaLion project. This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for the CubeSat developers.  This is particularly important when CubeSat projects are growing more numerous and with many of their respective team members being new to space systems development.   It has accomplished the ability to create individual elements of the architecture in an easily human readable code that is also easy to make revisions to.  Even for those who are unfamiliar with coding software or methods.  Thus, minimal training is required for usage.  It can also generate documents for easy presentation as well.Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.

>>>>

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Kevin Chiu, Sean Marquez, and Sharanabasaweshwara Asundi}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The SeaLion mission architecture team sought to create a model based systems engineering approach to assist improving CubeSat success rates as well as for the SeaLion CubeSat project to guide an implementation for the flight software.  Especially as university CubeSat teams grow in number but are characterized with having untrained students as their core personnel.  This was done using a document-as-code, or docs-as-code, approach.  With this the team created tools for the systems architecture with the Mach 30 Modeling Language to create a architecture that is easy to learn and use even for newly admitted team members with little to no training. These tools generate documents via its own code for easy presentaton on a local file system without any proprietary software while keeping model content format-agnostic.}

@@

Presented here is the systems engineering approach of the SeaLion CubeSat mission architecture.  This includes the modeling language, tools, and technical approach used to facilitate the configuration management, design, specification, and implementation of the SeaLion mission architecture for the flight software using a model-based approach.  Through, model-based systems engineering (MBSE), the SeaLion mission architecture team was able to create models, as opposed to documents, that serve as the authoritative source of truth for the conduction of system engineer activities \cite{architecting_spacecraft}.  These models were used to conduct activities such as design, specification, analysis, verification and validation of the system.  This was done by applying the NASA handbook on systems engineering \cite{nasa_handbook} to CubeSat mission design in efforts to facilitate a top-down design methodology from mission concept to specification of subsystem components, including flight software architecture \cite{asundi13_cubes}.  The approach presented herein had additional intents to make it was as simple and easy to use as possible.  This was done by a filesystem-based modelling language that adheres to expected patterns in agile software engineering (i.e., elements for stakeholder needs, user stories, data structures, etc.) using a lightweight YAML-based syntax.  This article also serves as an expansion of the conference proceedings (copyright held by Kevin Chiu and Sean Marquez) presented at American Institute of Aeronautics and Astronautics (AIAA) SciTech Forum 2023 \cite{scitech_proceeding}.

\subsection{CubeSat}
The CubeSat, originating from California Polytechnic State University in 1999, are a standardized form of nanosatellites.  Nanosatellites are satellites typically defined with a mass of less than 10 kg.  CubeSats, also known as Cube Satellites, are defined by the standardized and modular architecture of 1-Unit (1U) cube with dimensions of 10 cm X 10 cm X 10 cm with a mass of up to 2 kg \cite{cds_rev14}.  They can be scaled to 2-Units (2U), 3-Units (3U), or higher depending on units added as shown in figure \ref{fig:cubesat_family} with sizes designated by the CubeSat specification \cite{cds_rev14}.  This is done by the additional of standardized cube units to upscale the CubeSat.  The ability to scale by modularity gives a highly standardized structure for ease of expansion to provide versatility in functionality.  Due to their small size, mass, and lack of dedicated launch vehicles, CubeSats are typically launched as secondary payloads in conjunction with other larger satellites, informally known as “piggy-backing”.  This greatly decreases the cost of launching a CubeSat which greatly increases the accessibility of inserting objects into space.  As such, low budget groups such as universities have gravitated towards their use with increasing numbers \cite{swartwout_data}.  However, this presents challenges since many of the developers in universities are completely new to spacecraft development or systems engineering in general.

@@

The mission scope of having three payloads require special care and attention to ensure success of the mission.  However, many of the SeaLion project team members are new to spacecraft development and systems engineering.  Thus, the SeaLion mission architecture team took action to provide a mission architecture for the SeaLion team to better organize and direct the efforts of the team, to guide an implementation for the flight software, and to facilitate interface and assembly documentation.

@@

To address some of these issues, the SeaLion mission architecture team sought to help simplify the development process by providing readily available and easily learnable system engineering approaches and tools.  These provided system engineering approaches and tools include factors such as planning, documentation, project management, and simplifying the process.  Special attention should be given to systems engineering and information exchange for multidisciplinary teams \cite{aalto}.  To showcase these factor's importance, a survey conducted, by University of Bristol, on how to set up CubeSat projects of forty CubeSat groups emphasized the following relevant lessons learned \cite{howtosetup}:

@@

A MBSE approach was adopted by the Sealion CubeSat mission architecture team since it provided benefits such as reducing the ambiguity that usually comes with using informal language to specify systems or its various aspects.  It also minimized the duplication of content that tends to accumulate in a document-based system engineering approach.

Proper adoption of a MBSE approach also includes the selection of modeling language and modeling tool.  Considerations when selecting the modeling language and tool was overhead incurred from training the team, the technical overhead of setting up modelling tools, and future adaptability.  Refer to table \ref{tab:language} for modelling language down selection overview.  In addition, the Sealion CubeSat mission architecture team eventually decided to adopt a docs-as-code approach to further enhance the MBSE approach to achieve the listed goals shown above.

@@

Traditional approaches use documents as their authoritative source of truth for conducting system engineering activities \cite{architecting_spacecraft}.  Information in a traditional systems engineering approach today is mostly captured informally, not authored based on a methodology, configuration managed in silo tools, adhocly and infrequently integrated, not easily traceable to its provenance, not properly configuration managed, not properly changed managed, and not effectively shared with stakeholders \cite{caesar_model_based_approach}.  These documents often do not have a living relationship with other documents or to other corresponding elements; thus, changes to one document require manual changes to other documents \cite{ibm_mbse}.  Document-based approaches can exacerbate problems since it lacks point-to-point communication channels as well as lacking methods to enforce consistency \cite{call_herber_2022}.

In contrast, a MBSE approach supports capturing information in a highly structured modeling language, authored based on a methodology, configuration managed in a common tool, highly integrated, traceable to its provenance, and sharing with stakeholders.  MBSE solves the afformentioned issues with document-based approaches by providing models that have direct lines of communication to enforce that consistency.  Models providing the following key advantages over document-based approaches \cite{ibm_mbse}:

@@

As an example of the efficiency gains that MBSE can achieve with a side-by-side comparison between MBSE and non-MBSE approaches.  Using an architecting process, of 4,858 information element transfers, noted that all of these transfers were done manually with non-MBSE approaches; however, 13\% of these transfers with automated with MBSE with the potential of up to 81\% should it be used for trade study and peer review tasks \cite{younse_cameron_bradley_2021}.  The SeaLion mission architecture team seeks to take advantage of these efficiency gains that MBSE can achieve.  Usage of MBSE for space-related projects is not without precedent either.  Projects have been taking advantage of MBSE such as the ExoMars mission, Euclid, Galileo, and nanosatellite programs \cite{mazzini}, \cite{esa}, \cite{nottage_corns_2012}.  CubeSat projects have also been using MBSE and have shown to “hold promise of reducing the burden of system engineering tasks” and can “promote uniformity and consistency across future CubeSat models” \cite{kaslow}.  These attributes are important to reduce workload amongst team members and also to facilitate new team members as they join future projects.  Especially useful for universities since students are not available long term due to events such as graduation.

\subsection{Documents-As-Code Approach}
Documents-as-code (Docs-as-code) refers to a philosophy that team members should be writing documentation with the same tools as code \cite{ibm_mbse}.  This allows for documentation to updated seamlessly without additional work with document tools (doctools).  The code tools would include version control (e.g., Git), issues trackers, code tools (e.g., Visual Studio Code), etc.  To do so would mean that the “following the same workflows as development teams, and being integrated in the product team. It enables a culture where writers and developers both feel ownership of documentation, and work together to make it as good as possible” \cite{ibm_mbse}.  The SeaLion team taking advantage of the aforementioned philosophy would realize the benefits of utilizing the same principles and practices used to manage software, using modern version control tools (e.g., Git), for the configuration management of mission and flight software architecture documentation, and captured in a model-based approach \cite{ibm_mbse}.  In addition, these models can stored and used persistently on a local file system without the use of cloud based services.  Proprietary services are not required to generate documentation, modify documentation, or modify models.  Similar approaches have been seen as Structurizr \cite{structurizr} and F Prime Prime (FPP) \cite{f_prime_prime}.  FPP is based on F Prime which is an open-source software framework developed by NASA's Jet Propulsion Laboratory \cite{f_prime}.  While docs-as-code has precedent, the methodologies noted are not easily accesible to those without a sufficient background in programming.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modelling Language and Methodology}
The languages considered were SysML V1 \cite{sys_ml}, SysML V2 \cite{sys_ml2}, PlantUML \cite{plantuml}, and the Mach 30 modelling language (M30ML) \cite{mach30_git} with the mission architecture team conducting a trade study to determine the most suitable.  The down selection criteria that the SeaLion CubeSat mission architecture team has taken into consideration is shown in table \ref{tab:language}.

@@

\subsection{Ontological Modeling Language}
M30ML was developed using the Ontological Modeling Language (OML) as its basis.  OML is a language that enables defining systems engineering vocabularies and using them to describe systems \cite{oml_language}.  OML, inspired by Web Ontology Language 2 (OWL2) and the Semantic Web Rule Language (SWRL), is meant to be a more gentler and more disciplined method of aforementioned standard for use in systems engineering \cite{oml_language}.  OWL2 does not conform easily to individual modelling rules without tooling support; thus, OML was created.  OML is a tool to improve the speed of modeling and the quality of models while in a more concise and human-friendly high-level external representation \cite{oml_origin_and_rationale}.  However, more recently M30ML's development has been moved from OML to LinkML since it uses a lighter weight toolchain and YAML-based syntax \cite{linkml}.

@@

\subsection{Document Generation}
As noted multiple times throughout this article, there have been a number of figures and tables generated from the YAML files placed within the SeaLion mission architecture GitHub repository.  Many of the figures are UML diagrams that are auto-generated artifacts rendered from the M30ML modeling language and formatted using the Liquid template language.  This is the link for the docs-as-code approach.  YAML code files are used to generate documents for information sharing between group members.  This means that any changes made to the SeaLion mission architecture model can immediately be used to generate new documents.  Whether it be diagrams, tables, or text, continuous updating is ensured that any changes affecting dependencies within the mission architecture are kept in sync.  YAML files are automatically processed using templates langauge (e.g., Jinja2) via a build shell script.  This also means that content of the model and formatting of documents are decoupled.  The model is formatting-agnostic for documentation purposes as this is handled by template language.  A conference proceeding manuscript presented in AIAA SciTech 2023 was created purely by a docs-as-code format \cite{scitech_proceeding}.  The team used a LaTeX template to automatically format the manuscript to the conference guidelines and subsequently inject items such as the generated diagrams, tables, and references directly into the manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{M30ML Extensions for Component Implementation}
The implementation of M30ML for components, at the time of this article's publication, is currently in-process of integrating content information into the model.  A brief description of current component implementation into the SeaLion model is provided.  However, the model content mentioned herein is subjected to change.

\subsection{Distributed OSHW Framework}
  The current SeaLion mission architecture repository, at time of article publication, for components is “structured as a Distributed OSHW Framework (DOF) - component for defining the contents of the Mission concept of operations (ConOps) as a collection of nested subcomponents, component interfaces, and component functions for generating bill of materials (BOMs) and assembly instructions for the SeaLion CubeSat” \cite{sealion_mission_architecture}.  The DOF pillars are based on Open Source Hardware (OSHW) principals \cite{mach30_git}.  The implementation methodology presented herein is an extension of M30ML specifically for the use of modelling a CubeSat design.

  The SeaLion mission architecture repostiory has a components folder dedicated to its namesake.  Inside the components folder of the repository there are two subfolders; one labeled with 'sealion-cubesat' and another labeled with 'sealion-ground-station'.  Each of those folders would contain a components folder and subsequently those individual labeled components can have their own components folder.  Thus, a chain of components and subcomponents can be created as illustrated in figure \ref{fig:components_file}.  A parts YAML file in each components folder details what the subcomponents would be.  An excerpt example for the main SeaLion cubesat is provided in figure \ref{fig:components} that is associated with the file folders shown in figure \ref{fig:components_file}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
The SeaLion mission architecture team used MBSE with docs-as-code approach to the SeaLion project. This was done in efforts to reduce the friction and disconnect associated with traditional systems engineering for the CubeSat developers.  This is particularly important when CubeSat projects are growing more numerous and with many of their respective team members being new to space systems development.   It has accomplished the ability to create individual elements of the architecture in an easily human readable code that is also easy to make revisions to.  Even for those who are unfamiliar with coding software or methods.  Thus, minimal training is required for usage.  It can also generate documents for easy presentation as well.  Future work includes the components implementation as discussed in a prior section to faciliate interfaces and junctions for proper component relationships and planning.
